Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-10 Article/ici_submm_cloudcorr.tex
some more editing, cleaned up text and ref

Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems. In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to a present sensor: MWHS-2 (MicroWave humidity sounder 2). With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction. In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve. On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact. Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering. The resulting error distributions are almost symmetric with very low spread. The methodology also works well when only one of the higher frequencies (325\,GHz) is available. Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for each case individually. Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels. In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.

@@

Another motivation necessitating the need for cloud clearing is usage of 183\,GHz channels in 
numerical weather prediction (NWP). Usage of passive microwave data by
``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
but 183\,GHz data are still mainly used in a clear sky fashion
\citep{geer2018all}. The latter is particularly true in NWP of regional scope
\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
weather agencies will likely not be reached in many years. Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations. ``Scattering index'' \cite{geer2015scatteringindex} is one of the approaches used. It is based on brightness temperature differences between 89 and 150\,GHz. Another commonly used cloud filtering method is based on ``observation minus background'' (O-B), where the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.

Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean. This bias will translate to a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors. However this artificial suppression of observations diminishes the impact of observations. The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the assignment of uncertainty to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors have been provided. Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature also removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

The estimation of NFCS values makes use of a special type of machine learning,
denoted as Quantile Regression Neural Network (QRNN,
\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
only some kind of best estimate is provided, QRNN works in a Bayesian fashion
and instead gives a description of the posterior uncertainty. More precisely,
QRNN outputs an user specified set of quantiles that gives a discrete
description posterior distribution, that can be processed to derive e.g.\ the
expectation value.

The proposed cloud correction scheme makes use of a Quantile Regression Neural
Network (QRNN) to obtain a probabilistic prediction of the NFCS value. Unlike
traditional neural networks techniques, which typically only provide a point
estimate of the target variable, QRNNs are trained to predict an arbitrary set
of quantiles of its Bayesian a posteriori distribution
\citep{pfreundschuh:aneur:18}. The predicted a posteriori distribution 
can then be used to derive an estimate of the NFCS value together with an estimate
of the corresponding uncertainty.

The main focus of this study is the potential of proposed cloud-correction
method using sub-millimetre observations, which will become available
operationally with the launch of the Ice Cloud Imager (ICI,
\citet{eriksson:towar:20}) on board the next generation of polar orbiting
meteorological satellites (MetOP-SG), but will likely also be included in
several smaller missions (such as Artic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
observations at 89 and 150\ GHz channels (following
\citet{geer2015scatteringindex}), which are available already today. The focus
on sub-mm channels is motivated by several reasons. Firstly, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
signal than 183\,Ghz. In some cloudy situations it could be possible that the
impact at 183 GHz is of the order of thermal noise and modelling uncertainties,
while the impact at 325 GHz is significantly higher. Secondly, the proposed
cloud correction methods allows integrating ICI sub-mm observations in
clear-sky data assimilation schemes and thus provides a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}). The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global NWP models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}). For brevity, we assume that all simulations are mapped to a common footprint.

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.311    & 2000	&		\\
		AWS-33	&	178.811    & 2000 	&	\\
		AWS-34	&	180.311    & 1000 	&	\\
		AWS-35	&	181.511    & 1000 	&	 \\
		AWS-36	&	182.311    & \phantom{0}500  &	 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as European Space Agency (ESA)
Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels shall be included. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to
$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature \todo{$\ynfcs$, define it} at a given $183\unit{GHz}$ channel from a vector of
all-sky observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

QRNN's are trained to minimize the mean of the sum of the quantile loss functions
%
\begin{align}
\mathcal{L}_\tau(y_\tau, y) &=
\begin{cases}
\tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
\\
\end{cases}
\end{align}
%
for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data . The
quantile loss is used in this study as a performance criterion for the tuning of
the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution.

@@

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The
basic construction of both is that a separate network is trained for each
183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
output in both configurations is the posterior distribution of NFCS values for
the target 183\,GHz channel. The two configurations differ only by the number of
input 183\,GHz channels used in the training process:

@@

For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced later.

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to
gauge the complete performance. In a successful QRNN training, QRNN learns to
predict not only an accurate point estimates but also the correct underlying
uncertainty. An ideal QRNN output should be sharp or in other words, all
predicted quantiles should be concentrated in the vicinity of the point
estimate, but at the same time, the predicted posterior distribution should be
well calibrated, that is, the predicted distribution should reflect actually
observed frequencies. A straightforward way to compare the two distributions is
to plot the frequency of predictions and frequency of the true value in
different prediction intervals. This is also commonly known as calibration plot.
In a well-calibrated QRNN model, the calibration plot should follow the straight
line $y = x$. Another way to assess how well the predicted posterior distribution
reflects the observed errors is to compare the predicted and observed errors.
The predicted error is the deviation of a random sample drawn from the posterior
distribution to its median. In this study, we analyse both the calibration plot
and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results except hyper-parameter tuning, described in the study have been made on the test dataset. Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).

>>>>

Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems. In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear-sky (NFCS) radiances. The applicability of the approach is demonstrated by application to a present sensor: MicroWave Humidity Sounder-2 (MWHS-2). With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also analysed. The results are compared against the NFCS simulations. With the present sensors, the approach is partially successful in correcting the negative departures. Almost all cases with high cloud impact are corrected, but thin cirrus clouds cannot be fully corrected. In spite of the partial performance, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve. On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact. Only 2-6\% of the cases are partially corrected and these can be easily removed by a simple filtering. The resulting error distributions are almost symmetric with a very low spread. The methodology also works well when only one of the higher frequencies (325\,GHz) is available. Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for each case individually. Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels. In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.

@@

Another motivation necessitating the need for cloud clearing is usage of 183\,GHz channels in 
numerical weather prediction (NWP). Usage of passive microwave data by
``all-sky'' assimilation in global NWP is growing \citep{geer2017growing},
but 183\,GHz data are still mainly used in a clear-sky fashion
\citep{geer2018all}. The latter is particularly true in NWP of regional scope
\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
weather agencies will likely not be reached in many years. Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations. ``Scattering index'' \citep{geer2015scatteringindex} is one of the approaches used. It is based on brightness temperature differences between 89 and 150\,GHz. Another commonly used cloud filtering method is based on ``observation minus background'' (O-B), where the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.

Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean. This bias will translate to a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors. However this artificial suppression of observations diminishes the impact of observations. The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the assignment of uncertainty to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors have been provided. Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessary downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature also removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear-sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

The proposed cloud correction scheme makes use of a Quantile Regression Neural
Network (QRNN, \citet{pfreundschuh:aneur:18}) to obtain a probabilistic prediction of the NFCS value. Unlike traditional neural networks techniques, which typically only provide a point
estimate of the target variable, QRNNs are trained to predict an arbitrary set
of quantiles of its Bayesian a posteriori distribution
\citep{pfreundschuh:aneur:18}. The predicted a posteriori distribution 
can then be used to derive an estimate of the NFCS value together with an estimate
of the corresponding uncertainty.

The main focus of this study is the potential of proposed cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager (ICI,
\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
several smaller missions (such as Artic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
observations at 89 and 150\ GHz channels (following
\citet{geer2015scatteringindex}), which are available already today. The focus
on sub-mm channels is motivated by several reasons. Firstly, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
signal than 183\,GHz. In some cloudy situations it could be possible that the
impact at 183\,GHz is of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significantly higher. Secondly, the proposed
cloud correction methods allows integrating ICI sub-mm observations in
clear-sky data assimilation schemes and thus provides a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}). The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation). MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir). For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs. Therefore, a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (See Table~\ref{tab:ICI_MWI_channels}). For brevity, we assume that all simulations are mapped to a common footprint.

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.31    & 2000	&	0.45	\\
		AWS-33	&	178.81    & 2000 	&	0.45\\
		AWS-34	&	180.31    & 1000 	&	0.64\\
		AWS-35	&	181.51    & 1000 	&	0.64 \\
		AWS-36	&	182.31    & \phantom{0}500  &	0.88 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as European Space Agency (ESA)
Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels shall be included. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature \todo{$\ynfcs$} at a given $183\unit{GHz}$ channel from a vector of
all-sky observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

QRNN's are trained to minimize the mean of the sum of the quantile loss functions
%
\begin{align}
\mathcal{L}_\tau(y_\tau, y) &=
\begin{cases}
\tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
\\
\end{cases}
\end{align}
%
for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data . The
quantile loss is used in this study as a performance criterion for the tuning of
the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution.

@@

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The
basic construction of both is that a separate network is trained for each
183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
output in both configurations is the posterior distribution of $\ynfcs$ for
the target 183\,GHz channel. The two configurations differ only by the number of
input 183\,GHz channels used in the training process:

@@

For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent, and is described in detail when introduced later.

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. These examples illustrate the predicted quantiles for three different cases. The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for $\ynfcs$. To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to
gauge the complete performance. In a successful QRNN training, QRNN learns to
predict not only an accurate point estimate but also the correct underlying
uncertainty. An ideal QRNN output should be sharp or in other words, all
predicted quantiles should be concentrated in the vicinity of the point
estimate. Nevertheless, the predicted posterior distribution should also be
well calibrated, that is, the predicted distribution should reflect actually
observed frequencies. A straightforward way to compare the two distributions is
to plot the frequency of predictions and frequency of the true value in
different prediction intervals. This is also commonly known as calibration plot.
In a well-calibrated QRNN model, the calibration plot should follow the straight
line $y = x$. Another way to assess how well the predicted posterior distribution
reflects the observed errors is to compare the predicted and observed errors.
The predicted error is the deviation of a random sample drawn from the posterior
distribution to its median. In this study, we analyse both the calibration plot
and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the optimal experiment is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.
